Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
finished part b

Next, define $R_0 = R'$ and inductively define 
$$
R_i = \begin{cases}
	R_{i-1} &\text{ if }i \notin J\\
	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
\end{cases}$$
To prove (b), it suffices to show that elements of the form $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly indpendent, and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-vector space. These elements do not lie in $R_{i-1}$ because their order of pole at $Q_i$ is bigger than the order of any element in $R_{i-1}$, and are linearly independent amongst themselves because of injectivity of the linear map
\begin{align*}
	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
	e_i' & \subhalf{e_i'} \\
	e_i	 & \subhalf{e_i}
\end{pmatrix} 
\end{align*}

>>>>

Next, define $R_0 = R'$ and inductively define 
$$
R_i = \begin{cases}
	R_{i-1} &\text{ if }i \notin J\\
	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
\end{cases}$$
To prove (b), it suffices to show that elements of the form $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly indpendent, and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-vector space. These elements do not lie in $R_{i-1}$ because their order of pole at $Q_i$ is bigger than the order of any element in $R_{i-1}$, and are linearly independent amongst themselves because of injectivity of the linear map
\begin{align*}
	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
	e_i-2 & \frac{e_i-3}{2} \\
	e_i	 & \frac{e_i-1}{2}
\end{pmatrix} 
\end{align*}
The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the integer lattice points in the cone generated by the vectors $\left(e_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2} \right)$ is saturated, as the corresponding determinant is
\begin{align*}
	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
\end{align*}
completing part (b).

To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}
